---
title: "Untitled"
author: "First Last"
date: YYYY-MM-DD
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

Define V in global environment.

```{r define-v}
V <- 3
```

V is passed between chunks.

```{r print-v}
print(V)
```

V can be passed to anonymous functions that do not define it.

```{r anonymous-r}
Map(function(x) x + 1, V)
```

Using the "Knit" button in RStudio, `rmarkdown::render_site`, and
`rmarkdown::render`, V is passed to the function `undefined`, which references V
without defining it. However, `wflow_build`, which calls
`rmarkdown::render_site` via `callr::r_safe` does not allow this.


```{r try-to-use-V-in-package-function}
library("undefined")
undefined(1)
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
